D.I.A.G.R.A.M.: Digital Image Analysis for Graph Recognition And Modeling

### 2025-07-09 doc/article/article.tex
Updates

\subsubsection{Arrow-Text Association}
After a text box is assigned to an arrow, some computation is needed to fully understand how the text is associated to the arrow itself. The arrow is approximated by a line adjoining its head and its tail.
The distance between the line and the text's bounding box is computed and compared with a threshold - if it's over it, the association is discarded.
Otherwise, the line approximation is then split into three different sections - whose sizes are heuristically determined, such that the relation's central section is bigger than the other two. The distance between the text bounding box and each of the three sections boxes is computed - then, the section with the lowest distance value is then assigned to the text under consideration.
We must notice that for self-arrow we can not compute simple distance between the line and the text's bounding box, given that the approximated arrow line is not accurate. Thus, we approximate the arrow using two segments like a triangle.
The third point is the middle of the opposite edge. \\

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{arrowsplit.jpg}
	\caption{A three-split of an arrow.}
	\label{fig:arrowsplit}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{self_arrow.jpeg}
	\caption{Self-arrow approximation.}
	\label{fig:arrowsplit}
\end{figure}

@@

	% First row
	\begin{tabular}{ccc}
		\includegraphics[height=5cm]{ex6.png} &
		\includegraphics[height=5cm]{chat1.png} &
		\includegraphics[height=5cm]{chat2.png} \\
		% Optional captions under each image
		(a) Our result & (b) GPT Mermaid & (c) GPT D2 \\
	\end{tabular}

>>>>

\subsubsection{Arrow-Text Association}
After a text box is assigned to an arrow, some computation is needed to fully understand how the text is associated to the arrow itself. The arrow is approximated by a line adjoining its head and its tail.
The distance between the line and the text's bounding box is computed and compared with a threshold - if it's over it, the association is discarded.
Otherwise, the line approximation is then split into three different sections (see Figure~\ref{fig:arrowsplit}) - whose sizes are heuristically determined, such that the relation's central section is bigger than the other two. The distance between the text bounding box and each of the three sections boxes is computed - then, the section with the lowest distance value is then assigned to the text under consideration.
We must notice that for self-arrow we can not compute simple distance between the line and the text's bounding box, given that the approximated arrow line is not accurate. Thus, we approximate the arrow using two segments like a triangle.
The third point is the middle of the opposite edge (see Figure~\ref{fig:arrowapprox}). \\

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{arrowsplit.jpg}
	\caption{A three-split of an arrow.}
	\label{fig:arrowsplit}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{self_arrow.jpeg}
	\caption{Self-arrow approximation.}
	\label{fig:arrowapprox}
\end{figure}

@@

	% First row
	\begin{tabular}{ccc}
		\includegraphics[height=5cm]{ex6.png} &
		\includegraphics[height=5cm]{chat1.png} &
		\includegraphics[height=4.35cm]{chat2.png} \\
		% Optional captions under each image
		(a) Our result & (b) GPT Mermaid & (c) GPT D2 \\
	\end{tabular}
